### 2021-07-25 code/manuscript.Rmd
Fix tab1 reference

Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r fig1$anov["Part", "P1_f"]`, all *p*s `r fig1$anov["Part", "P1_p"]` (see Table \@ref(tab:tab1)).
In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r fig1$anov["Condition", "N400_df"]` = `r fig1$anov["Condition", "N400_f"]`, *p* = `r fig1$anov["Condition", "N400_p"]`.
Crucially, the part × condition interaction was significant in the N170 component, *F*`r tab1$anov["Pt. × con.", "N170_df"]` = `r tab1$anov["Pt. × con.", "N170_f"]`, *p* = `r tab1$anov["Pt. × con.", "N170_p"]`, and in the N400 component, *F*`r tab1$anov["Pt. × con.", "N400_df"]` = `r tab1$anov["Pt. × con.", "N400_f"]`, *p* `r tab1$anov["Pt. × con.", "N400_p"]` but not in the P1 component, *F*`r tab1$anov["Pt. × con.", "P1_df"]` = `r tab1$anov["Pt. × con.", "P1_f"]`, *p* = `r tab1$anov["Pt. × con.", "P1_p"]`.
To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.

>>>>

Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r tab1$anov["Part", "P1_f"]`, all *p*s `r tab1$anov["Part", "P1_p"]` (see Table \@ref(tab:tab1)).
In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r tab1$anov["Condition", "N400_df"]` = `r tab1$anov["Condition", "N400_f"]`, *p* = `r tab1$anov["Condition", "N400_p"]`.
Crucially, the part × condition interaction was significant in the N170 component, *F*`r tab1$anov["Pt. × con.", "N170_df"]` = `r tab1$anov["Pt. × con.", "N170_f"]`, *p* = `r tab1$anov["Pt. × con.", "N170_p"]`, and in the N400 component, *F*`r tab1$anov["Pt. × con.", "N400_df"]` = `r tab1$anov["Pt. × con.", "N400_f"]`, *p* `r tab1$anov["Pt. × con.", "N400_p"]` but not in the P1 component, *F*`r tab1$anov["Pt. × con.", "P1_df"]` = `r tab1$anov["Pt. × con.", "P1_f"]`, *p* = `r tab1$anov["Pt. × con.", "P1_p"]`.
To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
